---
title: "ttestdata_rmd"
author: "Wesley Gardiner"
date: "4/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(patchwork)
library(ggthemes)
```

Reading in the Data

```{r}
#Reading in the data (Sorry for the filepath)
data <- read.csv(here::here("data","raw","pdf_covid_data_election.csv"))                 

#Cleaning up the names
data <- 
  data %>% 
  mutate(state = as.character(state)) %>% 
  janitor::clean_names()

data$party <- factor(data$party, levels = c("republican","democrat"))


#Creating a republican filtered dataset
rep_data <- 
  data %>% 
  filter(party == "republican")


#Creating a democratic filtered 
dem_data <- 
  data %>% 
  filter(party == "democrat")

```

Now I need to extract the means of each activity

```{r}
rep_mean <-
  rep_data %>% 
  select(2:7) %>% 
  map(~ mean(.x, na.rm = TRUE)) %>% 
  as_tibble()

dem_mean <-
  dem_data %>% 
  select(2:7) %>% 
  map(~ mean(.x, na.rm = TRUE)) %>% 
  as_tibble()

```

Now I can start t-testing with the following hypothesis:

 * Hypothesis: Democratic states will move around less than republican states.
 * Null : Democratic states will move the same as republican states.

```{r}
#Hypothesis: Democratic states will move around less than republican states.
#Null : Democratic states will move the same as republican states.


#Creates tests for every activity
retail_ttest <- t.test(dem_data$retail_and_recreation, 
                       mu = rep_mean$retail_and_recreation[1], #Mean of republican States
                       alternative = "less", 
                       conf.level = 0.95)

groc_ttest <- t.test(dem_data$grocery_and_pharmacy, 
                     mu = rep_mean$grocery_and_pharmacy[1], #Mean of republican State
                     alternative = "less", 
                     conf.level = 0.95)

parks_ttest <- t.test(dem_data$parks, 
                      mu = rep_mean$parks[1], #Mean of republican State
                      alternative = "less", 
                      conf.level = 0.95)

transit_ttest <- t.test(dem_data$transit_stations, 
                        mu = rep_mean$transit_stations[1]	, #Mean of republican State
                        alternative = "less", 
                        conf.level = 0.95)

work_ttest <- t.test(dem_data$workplace, 
                     mu = rep_mean$workplace[1]	, #Mean of republican State
                     alternative = "less", 
                     conf.level = 0.95)

#I do a two sided t-test because if we think of the residential ascept of activies we would expect that residential would go up in activity from democratic states as apposed to going down (More people are going home/staying home than republican states.)


residential_ttest1 <- t.test(dem_data$residential, 
                             mu = rep_mean$residential[1]	, #Mean of republican State
                             alternative = "less",
                             conf.level = 0.95) 

residential_ttest2 <- t.test(dem_data$residential, 
                             mu = rep_mean$residential[1]	, #Mean of republican State
                             alternative = "two.sided",
                             conf.level = 0.95) 

#Creates a table for output
ttest <- tibble()
ttest <- 
  ttest %>% 
  rbind(tidy(retail_ttest)) %>% 
  rbind(tidy(groc_ttest)) %>% 
  rbind(tidy(parks_ttest)) %>% 
  rbind(tidy(transit_ttest)) %>% 
  rbind(tidy(work_ttest)) %>% 
  rbind(tidy(residential_ttest1)) %>% 
  rbind(tidy(residential_ttest2))

#Adds labels
ttest$activity = c("retail","groc","parks","transit","work","residential1","residential2")

#Cleans it up a little.
ttest <- 
  ttest %>% 
  select(activity, everything())

ttest
```

I do a two sided t-test because if we think of the residential ascept of activies we would expect that residential would go up in activity from democratic states as apposed to going down (More people are going home/staying home than republican states.)

As we can see from the `ttest` table, All the p-values are significant (excluding residential 1 being the one-sided ttest).


